A Connection Between Star Formation Rate and Dark Matter Halos at $Z\sim6$ In 2013 Planck Cosmology.

### 2015-02-20 paper/observations.tex
Paragraphs added to Observations: Mclure, Bouwens and Willott. Pending: Finkelstein

This paper is based on four main observational data sets. The most recent is
from the Hubble Space Telescope Legacy plus ground telescopes \citep{bouwens14}.
The second set is from the Canada-France Hawaii Telescope\citep{willott13} and
the last one by the UK Infrared Telescope and the Subaru Telescope
\cite{mclure09}. Those observations where made using the Drop-out technique.

The data from the HSTL is a compilation of previous works since
2006 \citep{bouwens06}, wich includes also observations after the 2009
upgrade mission\citep{bouwens12}. They estimate the uncertainty in their LF due
to cosmic variance. Taking account they used five independent surveys, they get
jus $\sigma\sim 10\%$\citep{bouwens14} using the Cosmic Variance Calculator
developed by Trenti \& Stiavelli (2008).

The dataset was retrieved from graphs for \cite{bouwens14} and \cite{mclure09} 
using
GAVO-DEXTER\footnote{\url{http://dc.zah.uni-heidelberg.de/dexter/ui/ui/custom}}.

Willott et al. \cite{willott13} presented the sixth release of the Canada-France-Hawaii Telescope Legacy Survey CFHTLS. The observations where performed over four separated fields covering a total area $\sim 4 \deg^2$ (a large area), it gives this survey great robustness.
Optical observations used MegaCam with $u^* g' r' i' z'$ filters. The main selection criteria: all the objects must be brighter than magnitude $z' = 25.3$. The final number of LBGs founded was 40. Moreover, they get spectroscopic confirmation for 7 candidates using GMOS spectrograph on the Gemini Telescopes, which has a field of view $\ll 1 \deg^2$. They show incompleteness in the sample due to foreground contamination and the detection algorithm; there is no warranty to have every object brighter than the limit magnitude on the faint limit. The full galaxy LF at $z=6$ cannot be obtained as in other studies. Nevertheless, this survey was focussed on the highly luminous LBGs. LF is calculated using the stepwise maximum likelihood method of Efstathiu et al. [Cite required!!!], within magnitudes from $M_{1350} = -22.5$ up to $-20.5$. The luminosity function of $z=5.9$ shows an exponential decline at the bright end, where feedback processes and inefficient last cooling limites star forming in bright galaxies hosted in the most massive halos.

@@

\subsection{The Drop-out Technique - Lyman Break Technique}

\cite{steidel03}

>>>>

This paper is based on four main observational data sets from the Hubble Space Telescope 
and three ground-based telescopes. All $z\sim 6$ LBG candidates where discovered using using 
the drop-out technique\citep{steidel03}. All magnitudes are in AB system.

The data from the Hubble Space Telescope Legacy (HSTL) \citep{bouwens14} is a compilation 
of observations since the installation of the Advanced Camera for Surveys (ACS) in 2002, 
through the near-infrared Wide Field Camera 3 (WFC3/IR) installed in 2009, up to 2012. 
The HST fields of view are: XDF, HUDF09-1, HUDF09-2, CANDELS-S/Deep, 
CANDELS-S/Wide, ERS, CANDELS-N/Deep, CANDELS-N/Wide, CANDELS-UDS, 
CANDELS-COSMOS and CANDELS-EGS, with areas of 4.7, 4.7, 4.7, 64.5, 34.2, 
40.5, 62.9, 60.9, 151.2, 151.9 and 150.7 arcmin$^2$ respectively. The total area corresponds 
to $\sim 0.7 \deg^2$ over five different lines of sight, reducing cosmic variance effects. 
Two cameras performed the observations: ACS and WFC3/IR, using 
$B_{435} V_{606} i_{814} z_{850} I_{814} Y_{098} Y_{105} J{125} JH_{140}$ and $H_{160}$ filters.
The limit magnitude is between $\sim27.5$mag in CANDELS-EGS and$\sim30 $mag in the 
deepest field (XDF). Total number of z=6 LBG candidates is 940, most of them in the faint 
end of the LF, magnitudes in the rest frame are in the range $-22.52\leq M_{1600} \leq -16.77$
The Schechter parameters derived are: $\phi^* / \textrm{Mpc}^{-3} =(0.33_{-0.10}^{+0.15}) \times 10 ^{-3}$, $M^*_{1600} = -21.16\pm 0.20$ and $\alpha = -1.91 \pm 0.09$. \citet{bouwens14} reported that using just few fields of view, UVLF has a slightly non-Schechter-like form.

\citet{willott13} presented the sixth release of the Canada-France-Hawaii 
Telescope Legacy Survey CFHTLS. The observations where performed over four 
separated fields covering a total area $\sim 4 \deg^2$ (a large area), it gives this 
survey great robustness. Optical observations used MegaCam 
[CITE REQUIRED] with $u^* g' r' i' z'$ filters. The main selection criteria: all the 
objects must be brighter than magnitude $z' = 25.3$. The final 
number of LBGs founded was 40. Moreover, they get spectroscopic confirmation 
for 7 candidates using GMOS spectrograph on the Gemini Telescopes, which 
has a $\ll 5.5$-square arcmin field of view . They show incompleteness in the sample due to 
foreground contamination and the detection algorithm; there is no warranty to 
have every object brighter than the limit magnitude on the faint limit. The full 
galaxy LF at $z=6$ cannot be obtained as in other studies. Nevertheless, this survey 
was focussed on the highly luminous LBGs. LF is calculated using the stepwise 
maximum likelihood method of Efstathiu et al. [MNRAS 1998 Cite required!!!], within 
magnitudes 
from $M_{1350} = -22.5$ up to $-20.5$. The luminosity function of $z=5.9$ shows 
an exponential decline at the bright end, where feedback processes and inefficient 
last cooling limites star forming in bright galaxies hosted in the most massive halos.

\citet{mclure09} build the luminosity function for $z=5$ and $z=6$ using data from two ground-based
 telescopes: the United Kingdom Infrared Telescope in the near-IR imaging and Subaru 
 Telescope for the optical imaging. They use the first data release of the UKIRT Infrared 
 DeepSky Survey Ultra Deep Survey (UDS), together with the Subaru XMM-Newton 
 Survey (SXDS). Total observed area is $0.63 \deg^2$ uniformly covered by booth catalogues.
The UKIRT was equipped with the WFCAM using $J K$ filters. The Subaru was equipped 
with the Suprime-Cam with the $B V R i' z'$ filters. All candidates where brighter than 
$z'=26$. The UV rest frame magnitude range is $-22.4\leq M_{1500} \leq-20.6$. The LF 
was calculated using the maximum likelihood estimator of Schmidt (1968). [Cite Required!!!!]. 
Their analysis gave a total number of 104 LBG candidates in the redshift range 
$5.7\leq z \leq 6.3$. LF was parameterized according to the Schechter function with 
$\phi^* / \textrm{Mpc}^{-3} =(1.8 \pm 0.5) \times 10 ^{-3}$, $M^*_{1500} = -20.04\pm 0.12$ 
and $\alpha = -1.71 \pm 0.11$.

The dataset was retrieved from \cite{mclure09} graph using
GAVO-DEXTER\footnote{\url{http://dc.zah.uni-heidelberg.de/dexter/ui/ui/custom}}.

Finkelstein
HST using CANDELS/GOODS fields, HUDF and Hubble Frontier Field deep parallel observations near the Abell 2744 and MACS J0416.1-2403 clusters. (Unlensend fields)

@@

%They estimate the uncertainty in their LF due
%to cosmic variance. Taking account they used five independent surveys, they get
%#jus $\sigma\sim 10\%$\citep{bouwens14} using the Cosmic Variance Calculator
%developed by Trenti \& Stiavelli (2008).

### 2015-02-20 paper/the_bibliography.tex
SFR, Fitting Model, The_Bibliography
adding references
Intro, Obs. data, SFR
Paragraphs added to Observations: Mclure, Bouwens and Willott. Pending: Finkelstein

\begin{thebibliography}{}
\bibitem[Bouwens(2006)]{bouwens06} Bouwens, R. J. et al. 2006, \apj, 653, 53	
		%2006ApJ...653...53B
\bibitem[Bouwens(2012)]{bouwens12} Bouwens, R. J. et al. 2012, \apj, 752, 5 	
		%2012ApJ...752L...5B
\bibitem[Bouwens(2014)]{bouwens14} Bouwens, R. J. et al. 2012, arXiv:1403.4295
\bibitem[Kennicutt(1998)]{kennicutt98} Kennicutt, Robert C., Jr. 1998, \araa, 
36, 189		%1998ARA&A..36..189K
\bibitem[Kennicutt(2009)]{kennicutt09} Kennicutt, Robert C., Jr et al. 2009, \apj, 
703, 4672	%2009ApJ...703.1672K
\bibitem[Law(2011)]{law11} Law, K. et al. 2011, \apj, 738, 124
		%2011ApJ...738..124L
\bibitem[McLure(2009)]{mclure09} McLure, R. J. et al. 2009, \mnras, 395, 2196	
		%2009MNRAS.395.2196M
\bibitem[Moster(2010)]{moster10} Moster, Benjamin P. et al. 2010, \apj, 710, 
903 
\bibitem[Riebe(2013)]{riebe13} Riebe, K. et al. 2013, AN, 334, 691 		
		%2013AN....334..691R
\bibitem[Steidel(2003)]{steidel03} Steidel, Charles C. et al. 2003, \apj, 592, 
728 		%2003ApJ...592..728S
\bibitem[Trimble(1987)]{trimble87} Trible, Virginia. 1987, \araa, 25, 425
\bibitem[Willott(2013)]{willott13} Willott, Chris J. et al. 2013, \aj, 145, 4	
		%2013AJ....145....4W

\end{thebibliography}

>>>>

\begin{thebibliography}{}

\bibitem[Bouwens(2006)]{bouwens06} Bouwens, R. J. et al. 2006, \apj, 653, 53	
		%2006ApJ...653...53B
\bibitem[Bouwens(2012)]{bouwens12} Bouwens, R. J. et al. 2012, \apj, 752, 5 	
		%2012ApJ...752L...5B
\bibitem[Bouwens et al.(2014)]{bouwens14} Bouwens, R. J., G. D. Illingworth, P. A. Oesch, M. Trenti, I. Labbe', L. Bradley, M. Carollo, et al.2014, arXiv:1403.4295

\bibitem[Kennicutt(1998)]{kennicutt98} Kennicutt, Robert C., Jr. 1998, \araa, 
36, 189		%1998ARA&A..36..189K
\bibitem[Kennicutt(2009)]{kennicutt09} Kennicutt, Robert C., Jr et al. 2009, \apj, 
703, 4672	%2009ApJ...703.1672K
\bibitem[Law(2011)]{law11} Law, K. et al. 2011, \apj, 738, 124
		%2011ApJ...738..124L
\bibitem[Jiang(2011)]{jiang11} Jiang, Linhua et al. 2011, \apj, 743, 65
		%2011ApJ...743...65J
\bibitem[Lee(2009)]{lee09} Lee, Kyoung-Soo et al. 2009, \apj, 695, 368
		%2009ApJ...695..368L
\bibitem[Lundgren(2014]{lundgren14} Lundgren, Britt F. et al, 2014, \apj, 780,
34		%2014ApJ...780...34L
\bibitem[Madau(1998)]{madau98} Madau, Piero. et al, 1998, \apj, 498, 106M
		%1998ApJ...498..106M
\bibitem[McLure et al.(2009)]{mclure09} McLure, R. J., M. Cirasuolo, J. S. Dunlop, S. Foucaud, \and O. Almaini. 2009, \mnras, 395, 2196	
		%2009MNRAS.395.2196M
\bibitem[Moster(2010)]{moster10} Moster, Benjamin P. et al. 2010, \apj, 710, 
903 
\bibitem[Riebe(2013)]{riebe13} Riebe, K. et al. 2013, AN, 334, 691 		
		%2013AN....334..691R
\bibitem[Steidel(2003)]{steidel03} Steidel, Charles C. et al. 2003, \apj, 592, 
728 		%2003ApJ...592..728S
\bibitem[Trimble(1987)]{trimble87} Trible, Virginia. 1987, \araa, 25, 425

\bibitem[van den Bosch(203)]{vandenbosch03} van den Bosh, Frank C. et al. 2003, \mnras,
40, 771		%2003MNRAS.340..771V
\bibitem[Willott et al.(2013)]{willott13} Willott, Chris J., Ross J. McLure, Pascale Hibon, Richard Bielby, Henry J. McCracken, Jean-Paul Kneib, Olivier Ilbert, David G. Bonfield, Victoria A. Bruce, \and Matt J. Jarvis. 2013, \aj, 145, 4	
		%2013AJ....145....4W
\end{thebibliography}
